Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
reference tweaks

\clearpage
\begin{thebibliography}{24}\raggedright
\bibitem[Alam \etal(2015)]{dr12}
Alam,~S., Albareti,~F.~D., Allende~Prieto,~C., \etal, 2015, \apjs, 219, 12
\bibitem[Bishop(2006)]{bishop}
Bishop,~C.~M., 2006, \textit{Pattern Recognition and Machine Learning}, Springer, New York
\bibitem[Blanco-Cuaresma \etal(2015)]{blancocuaresma}
Blanco-Cuaresma,~S., Soubiran,~C., Heiter,~U., \etal, 2015, \aap, 577, A47
\bibitem[Bovy(2015)]{bovy}
Bovy,~J., 2015, arXiv:1510.06745
\bibitem[Casey \etal(2016)]{casey16}
Casey,~A.~R., Hogg,~D.~W., Ness,~M., Rix,~H.-W., 2016, in preparation
\bibitem[De~Silva \etal(2015)]{galah}
De~Silva,~G.~M., Freeman,~K.~C., Bland-Hawthorn,~J., \etal, 2015, \mnras, 449, 2604
\bibitem[Font \etal(2006)]{font}
Font,~A.~S., Johnston,~K.~V., Bullock,~J.~S., Robertson,~B.~E., 2006, \apj, 638, 585 
\bibitem[Freeman \& Bland-Hawthorn(2002)]{freeman}
Freeman,~K., Bland-Hawthorn,~J., 2002, \araa, 40, 487
\bibitem[Garc{\'{\i}}a~P{\'e}rez \etal(2015)]{aspcap}
Garc{\'{\i}}a~P{\'e}rez,~A.~E., Allende~Prieto,~C., Holtzman,~J.~A., \etal, 2015, arXiv:1510.07635
\bibitem[Gilmore et al.(2012)]{gaiaeso} Gilmore, G., Randich, 
S., Asplund, M., et al.\ 2012, The Messenger, 147, 25 
\bibitem[Hunter(2007)]{matplotlib}
Hunter,~J.~D., 2007, Computing in Science \& Engineering, 9, 90
\bibitem[Jofr{\'e} \etal(2015)]{jofre} Jofr{\'e}, P., 
M{\"a}dler, T., Gilmore, G., et al.\ 2015, \mnras, 453, 1428 
\bibitem[Majewski \etal(2015)]{apogee}
Majewski,~S.~R., Schiavon,~R.~P., Frinchaboy,~P.~M., \etal, 2015, arXiv:1509.05420
\bibitem[Martell(2015)]{martell}
Martell,~S.~L., 2015, arXiv:1507.00079
\bibitem[Melendez \etal(2014)]{melendez}
Mel{\'e}ndez,~J., Ram{\'{\i}}rez,~I., Karakas,~A.~I., \etal, 2014, \apj, 791, 14
\bibitem[Mitschang \etal(2014)]{mitschang}
Mitschang,~A.~W., De~Silva,~G., Zucker,~D.~B., \etal, 2014, \mnras, 438, 2753
\bibitem[Ness \etal(2015)]{thecannon}
Ness,~M., Hogg,~D.~W., Rix,~H.-W., Ho,~A.~Y.~Q., Zasowski,~G., 2015, \apj, 808, 16
\bibitem[Ness \etal(2016a)]{ages}
Ness,~M., Hogg,~D.~W., Rix,~H.-W., \etal, 2016a, \apj, in press (arXiv:1511.08204)
\bibitem[Ness \etal(2016b)]{ness16}
Ness,~M., Hogg,~D.~W., Casey,~A.~R., Rix,~H.-W., 2016b, in preparation
\bibitem[Pedregosa \etal(2011)]{sklearn}
Pedregosa,~F., Varoquaux,~G., Gramfort,~A., \etal, 2011, Journal of Machine Learning Research, 12, 2825
\bibitem[Quillen \etal(2015)]{quillen}
Quillen,~A.~C., Anguiano,~B., De~Silva,~G., \etal, 2015, \mnras, 450, 2354
\bibitem[Ro{\v s}kar \etal(2008)]{roskar}
Ro{\v s}kar,~R., Debattista,~V.~P., Quinn,~T.~R., Stinson,~G.~S., Wadsley,~J., 2008, \apjl, 684, L79
\bibitem[Ting \etal(2016)]{ting}
Ting,~Y.-S., Conroy,~C., Rix,~H.-W., 2016, \apj, in press (arXiv:1507.07563)
\bibitem[van~der~Walt \etal(2011)]{numpy}
van~der~Walt,~S., Colbert,~S.~C., Varoquaux,~G., 2011, Computing in Science \& Engineering, 13, 22
\end{thebibliography}
\end{document}

>>>>

\clearpage
\begin{thebibliography}{24}\raggedright
\bibitem[Alam \etal(2015)]{dr12}
Alam,~S., Albareti,~F.~D., Allende~Prieto,~C., \etal, 2015, \apjs, 219, 12
\bibitem[Bishop(2006)]{bishop}
Bishop,~C.~M., 2006, \textit{Pattern Recognition and Machine Learning}, Springer, New York
\bibitem[Blanco-Cuaresma \etal(2015)]{blancocuaresma}
Blanco-Cuaresma,~S., Soubiran,~C., Heiter,~U., \etal, 2015, \aap, 577, A47
\bibitem[Bovy(2015)]{bovy}
Bovy,~J., 2015, arXiv:1510.06745
\bibitem[Casey \etal(2016)]{casey16}
Casey,~A.~R., Hogg,~D.~W., Ness,~M., Rix,~H.-W., 2016, in preparation
\bibitem[De~Silva \etal(2015)]{galah}
De~Silva,~G.~M., Freeman,~K.~C., Bland-Hawthorn,~J., \etal, 2015, \mnras, 449, 2604
\bibitem[Font \etal(2006)]{font}
Font,~A.~S., Johnston,~K.~V., Bullock,~J.~S., Robertson,~B.~E., 2006, \apj, 638, 585 
\bibitem[Freeman \& Bland-Hawthorn(2002)]{freeman}
Freeman,~K., Bland-Hawthorn,~J., 2002, \araa, 40, 487
\bibitem[Garc{\'{\i}}a~P{\'e}rez \etal(2015)]{aspcap}
Garc{\'{\i}}a~P{\'e}rez,~A.~E., Allende~Prieto,~C., Holtzman,~J.~A., \etal, 2015, arXiv:1510.07635
\bibitem[Gilmore \etal(2012)]{gaiaeso}
Gilmore,~G., Randich,~S., Asplund,~M., \etal, 2012, The Messenger, 147, 25 
\bibitem[Hunter(2007)]{matplotlib}
Hunter,~J.~D., 2007, Computing in Science \& Engineering, 9, 90
\bibitem[Jofr{\'e} \etal(2015)]{jofre}
Jofr{\'e},~P., M{\"a}dler,~T., Gilmore,~G., \etal, 2015, \mnras, 453, 1428 
\bibitem[Majewski \etal(2015)]{apogee}
Majewski,~S.~R., Schiavon,~R.~P., Frinchaboy,~P.~M., \etal, 2015, arXiv:1509.05420
\bibitem[Martell(2015)]{martell}
Martell,~S.~L., 2015, arXiv:1507.00079
\bibitem[Melendez \etal(2014)]{melendez}
Mel{\'e}ndez,~J., Ram{\'{\i}}rez,~I., Karakas,~A.~I., \etal, 2014, \apj, 791, 14
\bibitem[Mitschang \etal(2014)]{mitschang}
Mitschang,~A.~W., De~Silva,~G., Zucker,~D.~B., \etal, 2014, \mnras, 438, 2753
\bibitem[Ness \etal(2015)]{thecannon}
Ness,~M., Hogg,~D.~W., Rix,~H.-W., Ho,~A.~Y.~Q., Zasowski,~G., 2015, \apj, 808, 16
\bibitem[Ness \etal(2016a)]{ages}
Ness,~M., Hogg,~D.~W., Rix,~H.-W., \etal, 2016a, \apj, in press (arXiv:1511.08204)
\bibitem[Ness \etal(2016b)]{ness16}
Ness,~M., Hogg,~D.~W., Casey,~A.~R., Rix,~H.-W., 2016b, in preparation
\bibitem[Pedregosa \etal(2011)]{sklearn}
Pedregosa,~F., Varoquaux,~G., Gramfort,~A., \etal, 2011, Journal of Machine Learning Research, 12, 2825
\bibitem[Quillen \etal(2015)]{quillen}
Quillen,~A.~C., Anguiano,~B., De~Silva,~G., \etal, 2015, \mnras, 450, 2354
\bibitem[Ro{\v s}kar \etal(2008)]{roskar}
Ro{\v s}kar,~R., Debattista,~V.~P., Quinn,~T.~R., Stinson,~G.~S., Wadsley,~J., 2008, \apjl, 684, L79
\bibitem[Ting \etal(2016)]{ting}
Ting,~Y.-S., Conroy,~C., Rix,~H.-W., 2016, \apj, in press (arXiv:1507.07563)
\bibitem[van~der~Walt \etal(2011)]{numpy}
van~der~Walt,~S., Colbert,~S.~C., Varoquaux,~G., 2011, Computing in Science \& Engineering, 13, 22
\end{thebibliography}
\end{document}
